---
title: "Exploring the underlying Structures of Childhood Psychopathology"
author: "Auclstudent"
date: "26/11/2019"
---

```{r setup, include=FALSE }

knitr::opts_chunk$set(echo = TRUE)
#For Loading on External Drive - Change this to the location of your package files
source(self)

.libPaths(LIBPATH)
#Unhash the following comments to install relevant packages for this script
 install.packages("bannerCommenter")
 install.packages(foreign)
 install.packages(psych)
 install.packages(readr)
 install.packages(plotly)
 install.packages(car)
 install.packages("ppcor")
 install.packages(corrplot)
 install.packages("pracma")
 install.packages("qgraph")
 install.packages("parcor")
 install.packages("Matrix")
 install.packages("psych")
 install.packages("dplyr")
 install.packages("ggplot2")
 install.packages("bootnet")
 install.packages("networktools")
 install.packages("EGAnet")
 install.packages("igraph")
 install.packages("rmarkdown")
 install.packages("formattable")

library(bannerCommenter) #used solely for pretty boxes. Not necessary for analysis or processing
library(foreign)
library(psych)
library(readr)
library(plotly)
library(car)
library("ppcor")
library(corrplot)
library("pracma")
library("qgraph")
library("parcor")
library("Matrix")
library("psych")
library("dplyr")
library("ggplot2")
library("bootnet")
library("networktools")
library("EGAnet")
library("igraph")
library("rmarkdown")
library("tnet")
library("formattable")
library(kableExtra)

```


## Information on this script:

This script is intended to conduct a network analysis investigation
on selected measures of the ALSPAC Birth Cohort Study. The script is
designed to allow flexibilty in adding/removing variables into and out
of the network model. A novel feature added to this script is the 
separation of network connections by their weight in the network, and
and the capability to highlight only certain key nodes which bridge
categories or latent factors.

This script was created as part of a Dissertation project 
"Exploring the Underlying Structures of Comorbidity in Childhood 
Psychopathology: A Network Analysis of Symptom Relationships"   

This code was written by the author (auclstudent),
in partial fulfilment of the requirements for the degree of Psychology 
(BSc Hons).

Please contact the UCL Department of Psychology and Language Sciences, 
or the author if you wish to use this code. 
Unauthorised reproduction is not permitted.

DISCLAIMER: This code was written as a learning exercise and is still
in early development. Be sure to cut redundant code where necessary.

Please Note: This script operates on data that has already been processed and cleaned. 
             Please refer to the full version of this script for the data cleaning process.
             


```{r echo=FALSE,warning=F,message=F}

##...................................
## File location definitions
##...................................

nodefile=nodefileT1 # Holds location of file containing ALSPAC nodes and category labels for TimePoint 1

nodefile2=nodefileT2 # Holds location of file containing ALSPAC nodes and category labels for TimePoint 2

# IMPORTANT: Nodes listed in Nodefile and label files must be listed in parallel 

## default: for running as source
NF=nodefile
splitby=T1index #REMEMBER TO CHANGE ME :( 

##...................................
## Importing Datasets
##...................................

rawdataT1<-read.csv(T1_ALSPAC_Processed)[2:60]
rawdataT2<-read.csv(T2_ALSPAC_Processed)[2:60]

nodelist<-read.csv(NF)

# Collate all nodes in nodefile (e.g kr123)
allnodes<-as.vector(nodelist$node)

# Collate all categories of node (e.g "Hyperactivity")
allitems<-as.vector(nodelist$topic)
groups<-allitems

# Load parrallel list with individual labels for each node 
Names<-nodelist$label

```
# Descriptive statistics T1
```{r echo=FALSE,warning=F}
renamednodes<-colnames(rawdataT1)
DescSummaryT1<-NULL

# The following for loop creates a pretty table containing descriptive stats for all nodes in the network.

for(variable in 1:length(rawdataT1)){
  
  name<-renamednodes[variable]
  
  mean<-summary(rawdataT1[variable])[4]
  mean<-as.numeric(strsplit(mean,":")[[1]][2])
  mean<-toString(mean)
  
  sd<-sd(rawdataT1[[variable]],na.rm=TRUE)
  sd<-format(round(sd,3),nsmall = 3)
  sd<-toString(sd)
  
  mean<-paste0(mean,"(",sd,")")
  
  PP<-summary(rawdataT1[variable])[7]
  PP<-as.numeric(strsplit(PP,":")[[1]][2])
  PP=nrow(rawdataT1)-PP
  
  variable<-c(name,mean,PP)
  
  variable<-data.frame(Node=variable[1],Mean=variable[2],N=variable[3])
  DescSummaryT1<-rbind(DescSummaryT1,variable)
}

DescSummaryT1<-cbind(DescSummaryT1$Node,as.data.frame(Names),DescSummaryT1$Mean,DescSummaryT1$N)
colnames(DescSummaryT1)<-c("Node","Names","Mean(SD)","N")

DescSummaryT1 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")


```
# Descriptive statistics T2
```{r echo=FALSE,warning=F}
renamednodes<-colnames(rawdataT2)
DescSummaryT2<-NULL

# The following for loop creates a pretty table containing descriptive stats for all nodes in the network.

for(variable in 1:length(rawdataT2)){
  
  name<-renamednodes[variable]
  
  mean<-summary(rawdataT2[variable])[4]
  mean<-as.numeric(strsplit(mean,":")[[1]][2])
  mean<-toString(mean)
  
  sd<-sd(rawdataT2[[variable]],na.rm=TRUE)
  sd<-format(round(sd,3),nsmall = 3)
  sd<-toString(sd)
  
  mean<-paste0(mean,"(",sd,")")
  
  PP<-summary(rawdataT2[variable])[7]
  PP<-as.numeric(strsplit(PP,":")[[1]][2])
  PP=nrow(rawdataT2)-PP
  
  variable<-c(name,mean,PP)
  
  variable<-data.frame(Node=variable[1],Mean=variable[2],N=variable[3])
  DescSummaryT2<-rbind(DescSummaryT2,variable)
}

DescSummaryT2<-cbind(DescSummaryT2$Node,as.data.frame(Names),DescSummaryT2$Mean,DescSummaryT2$N)
colnames(DescSummaryT2)<-c("Node","Names","Mean(SD)","N")

DescSummaryT2 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")
```

## Research Question 1: Latent Factor Vs DSM comparison

# Results: Time Point 1
```{r echo=FALSE,warning=F,message=F}

## Results for Time Point 1 ##
## -------------------------------------------------------------------------------------------- ##

# The function below plots the network of symptoms according to their DSM CATEGORIES 

# The function Estimatenetwork is used as a wrapping function.
# Pairwise deletion is specified
# the EBICglasso method is used to estimate the network 

resultsT1<-estimateNetwork(rawdataT1,default = "EBICglasso", threshold= T,missing="pairwise") 

# -------------------------------- #

# The function below plots an equivalent network of the same symptoms, but generates categories using the walktrap clustering method - EGA

# inside the package EGA, the "glasso" model already uses the Extended BIC as a minimization criterion

EGA.graphT1<-EGA(data=rawdataT1,model="glasso",plot.EGA = F)

# Following this the groups extracted by the EGA network are sorted and placed into a seperate string for later use.

LgroupsT1<-c()
for(i in EGA.graphT1$wc){
  i<-toString(i)
  i<-paste("factor",i)
  LgroupsT1=c(LgroupsT1,i)}


```

Symptom Network: Categorised by DSM categories
```{r echo=FALSE,warning=F,message=F, fig.width=10, fig.height=6}

# Network plot of DSM network

# Custom colours are used. 

# layout="spring" instructs qgraph to use the Frutherman-reingold algorithim to organise the network plot.

DSM_Network_Plot_T1<-qgraph(resultsT1$graph,layout = "spring", labels = colnames(data), 
              groups = groups,
              details=T, minimum=0.1,cut=0.2,
              width = 6,
              height = 5,
              color = c("orangered","orange","springgreen3","slateblue","skyblue","red3",
                        "seagreen","sandybrown","violetred")
              )
```

Symptom Network: Latent Categories determined by EGA Clustering_Walktrap Algorithm
```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6}

# Network plot of EGA network

# Custom colours are used. 

# layout="spring" instructs qgraph to use the Frutherman-reingold algorithim to organise the network plot.

EGA_Network_Plot_T1<-qgraph(resultsT1$graph,layout = "spring", labels = colnames(data), 
              groups = LgroupsT1,
              details=T, minimum=0.1,cut=0.2,
              width = 6,
              height = 5,
               color = c("springgreen3","slateblue","violetred","orangered","sandybrown","red3","orange")
              )
```

# Results: Time Point 2
```{r echo=FALSE,warning=F,message=F}

## Results for Time Point 2 ##
## -------------------------------------------------------------------------------------------- ##

# The function below plots the network of symptoms according to their DSM CATEGORIES at TIME 2

# The function Estimatenetwork is used as a wrapping function.
# Pairwise deletion is specified
# the EBICglasso method is used to estimate the network 

resultsT2<-estimateNetwork(rawdataT2,default = "EBICglasso", threshold= T,missing="pairwise") 

# -------------------------------- #

# The function below plots an equivalent network of the same symptoms, but generates categories using the walktrap clustering method - EGA

# inside the package EGA, the "glasso" model already uses the Extended BIC as a minimization criterion

EGA.graphT2<-EGA(data=rawdataT2,model="glasso",plot.EGA = F)

# Following this the groups extracted by the EGA network are sorted and placed into a seperate string for later use.

LgroupsT2<-c()
for(i in EGA.graphT2$wc){
  i<-toString(i)
  i<-paste("factor",i)
  LgroupsT2=c(LgroupsT2,i)}
```

Symptom Network: Categorised by DSM categories
```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6}

# Network Plot of DSM network at Time 2. 

# Custom colours are used

# layout is fitted to the network structure at time 1 using layout = "..." 

DSM_Network_Plot_T2<-qgraph(resultsT2$graph, labels = colnames(data), 
              groups = groups,
              details=T, minimum=0.1,cut=0.2,
              width = 6,
              height = 5,
              layout= DSM_Network_Plot_T1$layout, # Force T1 & T2 graphs to have identical layouts
              color = c("orangered","orange","springgreen3","slateblue","skyblue","red3",
                        "seagreen","sandybrown","violetred")
              )
```

Symptom Network: Latent Categories determined by EGA Clustering_Walktrap Algorithm
```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6}

# Network Plot of EGA network at Time 2. 

# Custom colours are used

# layout is fitted to the network structure at time 1 using layout = "..." 

EGA_Network_Plot_T2<-qgraph(resultsT2$graph, labels = colnames(data), 
              groups = LgroupsT2,
              details=T, minimum=0.1,cut=0.2,
              width = 6,
              height = 5,
              layout= DSM_Network_Plot_T1$layout, # Force T1 & T2 graphs to have identical layouts
              color = c("slateblue","violetred","sandybrown","red3","orangered","springgreen3","seagreen","orange")
              )
```

Network Descriptives T1+T2
```{r echo=FALSE,warning=F,message=F,fig.width=25,fig.height=9}

# Other than grouping, the structure of the EGA network and DSM network are identical.

# Centrality statistics are derived from the DSM network, stored in resultsT1 and resultsT2

CentralityT1<-centrality_auto(resultsT1)
T1Between<-CentralityT1[["node.centrality"]][["Betweenness"]]
T1Between<-scale(T1Between)        # Scales centrality statistic to mean = 0, SD = 1 by default
T1Between<-as.data.frame(T1Between)

CentralityT2<-centrality_auto(resultsT2)
T2Between<-CentralityT2[["node.centrality"]][["Betweenness"]]
T2Between<-scale(T2Between)        # Scales centrality statistic to mean = 0, SD = 1 by default
T2Between<-as.data.frame(T2Between)

table<-T1Between
table<-cbind(colnames(resultsT1$graph),table)
table<-cbind(table,c(rep("T1",length(colnames(resultsT1$graph)))))
colnames(table)<-c("node","betweenness","timepoint")
table1<-table

table2<-T2Between
table2<-cbind(colnames(resultsT1$graph),table2)
table2<-cbind(table2,c(rep("T2",length(colnames(resultsT2$graph)))))
colnames(table2)<-c("node","betweenness","timepoint")

table<-rbind(table1,table2) # both tables are connected into one long table and plotted using ggplot

ggplot(table, aes(x=node, y=betweenness,fill=timepoint),height=10,width=10) + 
  geom_bar(stat = "identity",position=position_dodge()) + theme(axis.text = element_text(size=19),axis.text.x = element_text(angle=-90)) 


ggsave("plt.png", width = 25, height = 9, dpi = 120)



```

Creating plot of mean betweenness centrality per disorder category:

```{r, echo=FALSE,warning=F,message=F}
# Generating a summary of betweenness values for comparison with above plots 

table1<-as.data.frame(T1Between)
table1<-cbind(colnames(resultsT1$graph),table1)
table1<-cbind(table1,c(rep("T1",length(colnames(resultsT1$graph)))))
colnames(table1)<-c("node","betweenness","timepoint")

table2<-as.data.frame(T2Between)
table2<-cbind(colnames(resultsT2$graph),table2)
table2<-cbind(table2,c(rep("T2",length(colnames(resultsT1$graph)))))
colnames(table2)<-c("node","betweenness","timepoint")

Hmean<-mean(table1[1:5,2])
Hsd<-sd(table1[1:5,2])

IMmean<-mean(table1[6:9,2])
IMsd<-sd(table1[6:9,2])

INmean<-mean(table1[10:18,2])
INsd<-sd(table1[10:18,2])

SPAmean<-mean(table1[19:24,2])
SPAsd<-sd(table1[19:24,2])

SAmean<-mean(table1[25:30,2])
SAsd<-sd(table1[25:30,2])

Gmean<-mean(table1[31:37,2])
Gsd<-sd(table1[31:37,2])

Cmean<-mean(table1[38:45,2])
Csd<-sd(table1[38:45,2])

Dmean<-mean(table1[46:50,2])
Dsd<-sd(table1[46:50,2])

Emean<-mean(table1[51:59,2])
Esd<-sd(table1[51:59,2])

allmeans<-rbind(Hmean,IMmean,INmean,SPAmean,SAmean,Gmean,Cmean,Dmean,Emean)
allsds<-rbind(Hsd,IMsd,INsd,SPAsd,SAsd,Gsd,Csd,Dsd,Esd)

summary1<-as.data.frame(cbind(c(rep("T1",9))))
rownames(summary1)<-c("H","IM","IN","SPA","SA","G","C","D","E")
summary1<-cbind(rownames(summary1),summary1)
summary1<-cbind(summary1,as.numeric(allmeans),as.numeric(allsds))
colnames(summary1)<-c("category","timepoint","mean","Sd")

Hmean<-mean(table2[1:5,2])
Hsd<-sd(table2[1:5,2])

IMmean<-mean(table2[6:9,2])
IMsd<-sd(table2[6:9,2])

INmean<-mean(table2[10:18,2])
INsd<-sd(table2[10:18,2])

SPAmean<-mean(table2[19:24,2])
SPAsd<-sd(table2[19:24,2])

SAmean<-mean(table2[25:30,2])
SAsd<-sd(table2[25:30,2])

Gmean<-mean(table2[31:37,2])
Gsd<-sd(table2[31:37,2])

Cmean<-mean(table2[38:45,2])
Csd<-sd(table2[38:45,2])

Dmean<-mean(table2[46:50,2])
Dsd<-sd(table2[46:50,2])

Emean<-mean(table2[51:59,2])
Esd<-sd(table2[51:59,2])

allmeans<-rbind(Hmean,IMmean,INmean,SPAmean,SAmean,Gmean,Cmean,Dmean,Emean)
allsds<-rbind(Hsd,IMsd,INsd,SPAsd,SAsd,Gsd,Csd,Dsd,Esd)

summary2<-as.data.frame(cbind(c(rep("T2",9))))
rownames(summary2)<-c("H","IM","IN","SPA","SA","G","C","D","E")
summary2<-cbind(rownames(summary2),summary2)
summary2<-cbind(summary2,as.numeric(allmeans),as.numeric(allsds))
colnames(summary2)<-c("category","timepoint","mean","Sd")

CategorySummary<-rbind(summary1,summary2)
CategorySummary<-as.data.frame(CategorySummary)

ggplot(CategorySummary, aes(x=category, y=mean, fill=timepoint)) + 
  geom_bar(stat="identity", color="black",position = position_dodge())+ 
  geom_errorbar(aes(ymin=mean-Sd, ymax=mean+Sd), width=.2,
                 position=position_dodge(.9)) + theme(axis.text = element_text(size=15),axis.text.x = element_text(angle=0)) 

```


Network Descriptives calculated using Expected Influence

```{r echo=FALSE,warning=F,message=F,fig.width=25,fig.height=9}

table1=NULL
table2=NULL


bridgeout1<-bridge(resultsT1$graph,communities = allitems)
EI2network1<-as.data.frame(scale(bridgeout1$`Bridge Expected Influence (2-step)`))
ScaledBetween1<-scale(T1Between,center = 0)

table1<-cbind(colnames(resultsT1$graph),EI2network1,ScaledBetween1,c(rep("T1",length(colnames(resultsT1$graph)))))
colnames(table1)<-c("node","EI2","Betweenness","timepoint")

bridgeout2<-bridge(resultsT2$graph,communities=allitems)
EI2network2<-as.data.frame(scale(bridgeout2$`Bridge Expected Influence (2-step)`))
ScaledBetween2<-scale(T2Between,center = 0)

table2<-cbind(colnames(resultsT2$graph),EI2network2,ScaledBetween2,c(rep("T2",length(colnames(resultsT2$graph)))))
colnames(table2)<-c("node","EI2","Betweenness","timepoint")

table<-rbind(table1,table2)



table1$name <- factor(table1$node, levels = table1$node[order(table1$EI2)])
table2$name <- factor(table2$node, levels = table2$node[order(table2$EI2)])


table1sorted <- table1[order(-table1$EI2),]
table2sorted <- table2[order(-table2$EI2),]



ggplot(data=table1,aes(x=name,group=1)) + 
  geom_point(aes(y=EI2),shape=2) +
  geom_point(aes(y=Betweenness)) +
  geom_line(aes(y=EI2),colour="red") +
  geom_line(aes(y=Betweenness),colour="blue") +
  theme(axis.text = element_text(size=15),axis.text.x = element_text(angle=-90)) + 
  ylab("Centrality Score") +
  xlab("Node Name") +
  ggtitle("A. Betweenness Centrality and Two-Step Expected Influence (EI2) per Symptom node at Time point 1") +
  theme(axis.text = element_text(size=15),
        axis.text.x = element_text(angle=-90),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        plot.title = element_text(size=20))


ggplot(data=table2,aes(x=name,group=1)) + 
  geom_point(aes(y=EI2),shape=2) +
  geom_point(aes(y=Betweenness)) +
  geom_line(aes(y=EI2),colour="red") +
  geom_line(aes(y=Betweenness),colour="blue") +
  theme(axis.text = element_text(size=15),axis.text.x = element_text(angle=-90)) + 
  ylab("Centrality Score") +
  xlab("Node Name") +
  ggtitle("B. Betweenness Centrality and Two-Step Expected Influence (EI2) per Symptom node at Time point 2") +
  theme(axis.text = element_text(size=15),
        axis.text.x = element_text(angle=-90),
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        plot.title = element_text(size=20))


table %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

```


Network Descriptive Comparisons

```{r echo=FALSE,warning=F,message=F}

tNETresults<-tnet::as.tnet(resultsT1$graph) #tnet is used as a way to easily match the node column names to their centrality values:
#their presentation of information in their output is more readable

#Calculating node average Betweenness
Betweeness<-as.data.frame(tnet::betweenness_w(tNETresults))#Betweenness calculation
rownames(Betweeness)<-resultsT1[["labels"]]

#Calculating node average Closeness
Closeness<-as.data.frame(tnet::closeness_w(tNETresults))#Closeness calculation
rownames(Closeness)<-resultsT1[["labels"]]

#Calculating the sum scores for each column (node) within the data.
frequencytable<-colSums(rawdataT1,na.rm=T)      #NOTE:The name Frequency table is *wrong* it is actually a weighted sum score per node
frequencytable<-as.data.frame(frequencytable)

#Calculating Descriptive Stats

NetworkBetweenAvg<-sum(Betweeness$betweenness)/resultsT1$nNode
NetworkBetweenAvg<-toString(NetworkBetweenAvg)

NetworkBetweenSD<-sd(Betweeness$betweenness)
NetworkBetweenSD<-toString(NetworkBetweenSD)

NetworkBetweenAvg<-paste0(NetworkBetweenAvg,"(",NetworkBetweenSD,")")


NetworkCloseAvg<-sum(Closeness$closeness)/resultsT1$nNode
NetworkCloseAvg<-toString(NetworkCloseAvg)

NetworkcloseSD<-sd(Closeness$closeness)
NetworkcloseSD<-toString(NetworkcloseSD)

NetworkCloseAvg<-paste0(NetworkCloseAvg,"(",NetworkcloseSD,")")


totalNodeStrength<-sum(abs(resultsT1$graph))
averageNodeStrength<-totalNodeStrength/resultsT1$nNode
averageNodeStrength<-toString(averageNodeStrength)

SDedgeWeight<-sd(abs(resultsT1$graph))
SDedgeWeight<-toString(SDedgeWeight)

averageNodeStrength<-paste0(averageNodeStrength,"(",SDedgeWeight,")")

NetworkAverageT1<-c(NetworkBetweenAvg,NetworkCloseAvg,averageNodeStrength)

Descriptives<-c("Betweenness","Closeness","Edge Strength")

NetDescriptives1<-as.data.frame(Descriptives)
NetDescriptives1<-cbind(NetDescriptives1,as.data.frame(NetworkAverageT1))

##########################################################################


tNETresults<-tnet::as.tnet(resultsT2$graph) #tnet is used as a way to easily match the node column names to their centrality values:
#their presentation of information in their output is more readable

#Calculating node average Betweenness
Betweeness<-as.data.frame(tnet::betweenness_w(tNETresults))#Betweenness calculation
rownames(Betweeness)<-resultsT2[["labels"]]

#Calculating node average Closeness
Closeness<-as.data.frame(tnet::closeness_w(tNETresults))#Closeness calculation
rownames(Closeness)<-resultsT2[["labels"]]

#Calculating the sum scores for each column (node) within the data.
frequencytable<-colSums(rawdataT2,na.rm=T)      #NOTE:The name Frequency table is *wrong* it is actually a weighted sum score per node
frequencytable<-as.data.frame(frequencytable)

#Calculating Descriptive Stats

NetworkBetweenAvg<-sum(Betweeness$betweenness)/resultsT2$nNode
NetworkBetweenAvg<-toString(NetworkBetweenAvg)

NetworkBetweenSD<-sd(Betweeness$betweenness)
NetworkBetweenSD<-toString(NetworkBetweenSD)

NetworkBetweenAvg<-paste0(NetworkBetweenAvg,"(",NetworkBetweenSD,")")


NetworkCloseAvg<-sum(Closeness$closeness)/resultsT2$nNode
NetworkCloseAvg<-toString(NetworkCloseAvg)

NetworkcloseSD<-sd(Closeness$closeness)
NetworkcloseSD<-toString(NetworkcloseSD)

NetworkCloseAvg<-paste0(NetworkCloseAvg,"(",NetworkcloseSD,")")


totalNodeStrength<-sum(abs(resultsT2$graph))
averageNodeStrength<-totalNodeStrength/resultsT2$nNode
averageNodeStrength<-toString(averageNodeStrength)

SDedgeWeight<-sd(abs(resultsT2$graph))
SDedgeWeight<-toString(SDedgeWeight)

averageNodeStrength<-paste0(averageNodeStrength,"(",SDedgeWeight,")")

NetworkAverageT2<-c(NetworkBetweenAvg,NetworkCloseAvg,averageNodeStrength)

Descriptives<-c("Betweenness","Closeness","Edge Strength")


NetDescriptives2<-cbind(as.data.frame(NetworkAverageT2))

t<-cbind(NetDescriptives1,NetDescriptives2)

t %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")
```

Smallworld Estimation

```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6}

# Estimation not used in final report. 

# Cannot get this to work without taking 100,000 years. Currently ignored pending further use in later projects.

set.seed(100)
#smallworldness(resultsT1)

#smallworldness(resultsT2)

```



## Research Question 2: Investigating Comorbid Symptoms connecting disorders


```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6} 

source('E:/MyRSpace/2019_Dissertation/analysis/settings/flowerplot.R')

# NOTE: This section requires flowerplot() function to be defined:

# flowerplot() is a custom function created for the analysis within this study only. Please refer to the .txt file in
# "E:\MyRSpace\2019_Dissertation\analysis\settings" for documentation on the operation and use of this function.

# Results @Time point 1
Heat1<-flowerplot(resultsT1$graph,seperator=".",unrelated_edge_colour = "grey",graphtitle = "Heatmap of Significant Connections at Time Point 1",graphlayout = DSM_Network_Plot_T1$layout, n=resultsT1$nPerson)

# Results @Time point 2
Heat2<-flowerplot(resultsT2$graph,seperator=".",unrelated_edge_colour = "grey",graphtitle = "Heatmap of Significant Connections at Time Point 2",graphlayout = DSM_Network_Plot_T1$layout, n=resultsT2$nPerson)

```

Seperation of disorder symptoms by DSM category: Contrasting connections between Internalising, Externalising and compulsive disorders:

Time Point 1
```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6} 

H=colnames(resultsT1$graph)[1:5]
IM=colnames(resultsT1$graph)[6:9]
IN=colnames(resultsT1$graph)[10:18]
E=colnames(resultsT1$graph)[51:59]

SPA=colnames(resultsT1$graph)[19:24]
SA=colnames(resultsT1$graph)[25:30]
G=colnames(resultsT1$graph)[31:37]
D=colnames(resultsT1$graph)[46:50]

C=colnames(resultsT1$graph)[38:45]

Internalising=c(SPA,SA,G,D)
Externalising=c(E,IM,IN,H)

# NOTE: This section requires flowerplot() function to be defined:
# -----------------------------------------------------------------------------------------------------------------------
# Results @Time point 1

F1.c<-flowerplot(resultsT1$graph,seperator = ".",C,graphlayout="groups",qgraphgroups = groups, overridecolour = TRUE, graphtitle = "Compulsions T1", n=resultsT1$nPerson)

# Results @time point 2

F2.c<-flowerplot(resultsT2$graph,seperator = ".",C,graphlayout="groups",qgraphgroups = groups, overridecolour = TRUE, graphtitle = "Compulsions T2", n = resultsT2$nPerson)



```


```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6}

F1.I<-flowerplot(resultsT1$graph,seperator = ".",Internalising,graphlayout="groups",qgraphgroups = groups,overridecolour=TRUE,graphtitle = "Internalising T1",n=resultsT1$nPerson)

F1.E<-flowerplot(resultsT1$graph,seperator = ".",Externalising,graphlayout="groups",qgraphgroups = groups,overridecolour=TRUE,graphtitle = "Externalising T1",n=resultsT1$nPerson)

F2.I<-flowerplot(resultsT2$graph,seperator = ".",Internalising,graphlayout="groups",qgraphgroups = groups,overridecolour=TRUE,graphtitle = "Internalising T2",n=resultsT2$nPerson)

F2.E<-flowerplot(resultsT2$graph,seperator = ".",Externalising,graphlayout="groups",qgraphgroups = groups,overridecolour=TRUE,graphtitle = "Exteranlising T2",n=resultsT2$nPerson)

```

Further Investigation of Compulsive Nodes only

Time 1
```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6}

# A seperate connection splot is created for each node within the network. 

# NOTE: this analysis is not included within the final dissertation report. 

C.1<-flowerplot(resultsT1$graph,seperator = ".",
             "C.1",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.1 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.2<-flowerplot(resultsT1$graph,seperator = ".",
             "C.2",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.2 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.3<-flowerplot(resultsT1$graph,seperator = ".",
             "C.3",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.3 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.4<-flowerplot(resultsT1$graph,seperator = ".",
             "C.4",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.4 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.5<-flowerplot(resultsT1$graph,seperator = ".",
             "C.5",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.5 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.6<-flowerplot(resultsT1$graph,seperator = ".",
             "C.6",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.6 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.7<-flowerplot(resultsT1$graph,seperator = ".",
             "C.7",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)
C.7 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.8<-flowerplot(resultsT1$graph,seperator = ".",
             "C.8",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)
C.8 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")


```

Time 2


```{r echo=FALSE,warning=F,message=F,fig.width=10, fig.height=6}
C.1<-flowerplot(resultsT2$graph,seperator = ".",
             "C.1",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.1 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.2<-flowerplot(resultsT2$graph,seperator = ".",
             "C.2",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.2 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.3<-flowerplot(resultsT2$graph,seperator = ".",
             "C.3",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.3 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.4<-flowerplot(resultsT2$graph,seperator = ".",
             "C.4",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.4 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.5<-flowerplot(resultsT2$graph,seperator = ".",
             "C.5",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.5 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.6<-flowerplot(resultsT2$graph,seperator = ".",
             "C.6",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)

C.6 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.7<-flowerplot(resultsT2$graph,seperator = ".",
             "C.7",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)
C.7 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")

C.8<-flowerplot(resultsT2$graph,seperator = ".",
             "C.8",graphlayout="groups",
             qgraphgroups = groups, 
             overridecolour = TRUE, 
             n = resultsT1$nPerson)
C.8 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("condensed"),full_width = F,position="left")


```

